---
title: "Problem Set 3 - Soriano"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r boilerplate, include=FALSE}
##Boilerplate Items for BDS##
library("tidyverse") 
library("psych")
library("haven")
library("flexsurv")
library("foreign")
library("survival")
library("flexsurv")
rm(list=ls())

#Setup the data directories(different kinds)
df<-read.csv ("ccg803.csv")
source("fitparametric.R")
```

# Problem 1a.
The exponentiated coeffecient for rx is 0.73, which represenets the HR between control and treatment group. The odds of recurrence of leukemia in those that receive dactinomycin in addition to standard therapy is 27% lower than those that undergo standard therapy. 95% confidence interval for the hazard ratio is (0.55-0.99)

# Problem 1b
After adjusting for age and white blood cell count, the exponentiated coefficient for rx is 0.74, with a 95% CI (0.55- 1.0) 

# Problem 1c


```{r, results=TRUE}
### 1a
s.df = with(df, Surv(duration, relapse))
coxFit.1a = coxph(s.df ~ rx, data=df)
summary (coxFit.1a)

### 1b
coxFit.1b = coxph(s.df ~ rx + wbc + age, data=df)
summary(coxFit.1b)

### 1c
# dichotomize WBC based on the cutoff of 100
df$wbcHigh [df$wbc >= 99] <- 1
df$wbcHigh [df$wbc < 100] <- 0
summary(coxph(s.df ~ rx + wbc + age + strata(wbcHigh), data=df))

### 1d
summary(coxph(s.df ~ rx + wbc + age + strata(institution), data=df))

### 1e
coxFit.1e = coxph(s.df ~ rx, data=df, ties="exact")
plot (survfit(coxFit.1e,newdata=data.frame(rx=1),conf.type="none"), col=2,lwd=2)
lines(survfit(coxFit.1e,newdata=data.frame(rx=0),conf.type="none"),col=4,lwd=2)
legend("bottomleft",fill=c(2,4),legend=c("Treatment","control"),bty='n')

# profile1=data.frame(wbc40=1,wbc200=0)
# profile2=data.frame(wbc40=0,wbc00=1)
# coxFit.1e = coxph(s.df ~ rx + df$age==5 + wbc40 + wbc200, data=df, ties="exact")
# plot (survfit(coxFit.1e,newdata=profile1,conf.type="none"), col=2,lwd=2)
# lines(survfit(coxFit.1e,newdata=data.frame(rx=0),conf.type="none"),col=4,lwd=2)
# legend("bottomleft",fill=c(2,4),legend=c("Treatment","control"),bty='n')

```
# PROBLEM 2

```{r}
#setup
addicts<-read.csv ("addicts.csv")
source("fitparametric.R")
```

```{r}
##Problem 2a
s.addicts = with(addicts, Surv(time, event))
coxFit.2a = coxph(s.addicts ~ dose + prison + clinic, data=addicts)
summary (coxFit.2a)

##Problem 2b
coxFit.2b = coxph(s.addicts ~ dose + prison + strata(clinic), data=addicts)
summary (coxFit.2b)

##Problem 2c
coxFit.2c = coxph(s.addicts ~ dose + prison + strata(clinic) + prison*dose, data=addicts)
summary (coxFit.2b)



```
