---
title: "Problem Set 3 - Soriano"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r boilerplate, include=FALSE}
##Boilerplate Items for BDS##
library("tidyverse") 
library("psych")
library("haven")
library("flexsurv")
library("foreign")
library("survival")
library("flexsurv")
rm(list=ls())

#Setup the data directories(different kinds)
df<-read.csv ("ccg803.csv")
source("fitparametric.R")
```

# PROBLEM 1a.

```{r, results=TRUE}
# 1a
s.df = with(df, Surv(duration, relapse))
df.cox.1a = coxph(s.df ~ rx, data=df)
summary (df.cox.1a)

# 1b
df.cox.1b = coxph(s.df ~ rx + wbc + )

```
# Problem 2c
2c.i. Plot is below

2c.ii. Subjectively, there appears to be a significant difference between the two groups. However, when I plotted the confidence intervals, there was a bit of overlapp, so with a forma analysis, there may not be significant diference in instantaneous risk at 8 months.

2c.iii. The distribution of time until exit from maintenance does not differ signficantly by history of incarceration (p=0.3) 

2c.iv. Based on the Z-column, none of the paramenters would be considered significant. Thus, I would state that based on the W-G-B test, there is no significant difference in the distribution of time to failure by history of incarceration.

2c.v.  Hazard functions are crossing, which worsens the power of our logrank test. Not as clear how this would affect the expeted differences in our chi-square test.

```{r}
##Save for coding question later
#prisonY <- survfit(Surv(time,event)~1,data=addicts[addicts$prison==1,], conf.type="log-log")
#prisonN <- survfit(Surv(time,event)~1,data=addicts[addicts$prison==0,], conf.type="log-log")
#question 2c.iii -- wording 

#2c.i and 2c.ii
prison<- survfit(Surv(time,event)~prison,data=addicts, conf.type="log-log")
plot(prison, col=c("blue","orange"), conf.int = FALSE,
     mark.time=TRUE,
     xlab="Time (days)",ylab="Survival Probability",lwd=1.5)
legend ("topright", c("No Prison", "Prison"), col=c("blue","orange"), lwd=c(2,2), cex=1.2)

#2c.iii.
s.prison <- with(addicts, Surv(time, event))
survdiff (s.prison ~ prison, data=addicts)

#2c.iv
library(survMisc)
comp(ten(prison))$tests$lrTests

#2c.v.
plot(prison, fun="cumhaz",
      xlab="Time(days)", ylab="Cumulative hazard", main="Nelson-Aalen cumulative hazard estimates",
      col=c("blue", "orange"), lwd=2)

```

# Problem 2d
2d.i. Plot is below

2c.ii. Subjectively, there appears to be a significant difference between the two groups.When plotting the CIs, with the exception of a smaller segment of time, the intervals do not seem to cross between the two groups.

2c.iii. The distribution of time until exit from maintenance does  differ significantly by methadone dose levels (p<< 0.01) 

2c.iv. Based on the Z-column, all of the paramenters would be considered significant. 

2c.v.  Hazard functions appear to splay quite a bit near the end of the observation period. 


```{r, results=TRUE}

#2di. and ii.
#Create binary variable 'highdose' with results---  1 for >60mg, 0 for <=60
addicts$highdose<- as.numeric(addicts$dose>60)

methadone <- survfit(Surv(time,event)~highdose,data=addicts, conf.type="log-log")
plot(methadone, col=c("blue","orange"), conf.int = TRUE,
     mark.time=TRUE,
     xlab="Time (days)",ylab="Survival Probability",lwd=1.5)
legend ("topright", c("Low Dose (60 or less)", "High dose (>60)"), col=c("blue","orange"), lwd=c(2,2), cex=1.2)

#2d.iii.
s.methadone <- with(addicts, Surv(time, event))
survdiff (s.methadone ~ highdose, data=addicts)

#2d.iv
library(survMisc)
comp(ten(methadone))$tests$lrTests

#2d.v.
plot(methadone, fun="cumhaz",
      xlab="Time(days)", ylab="Cumulative hazard", main="Nelson-Aalen cumulative hazard estimates",
      col=c("blue", "orange"), lwd=2)
legend ("topleft", c("Low Dose (60 or less)", "High dose (>60)"), col=c("blue","orange"), lwd=c(2,2), cex=1.2)



```
# Problem 2e
Sorry, I ran out of time to learn superscripts and subscribts in rmd, to I'll just have to talk it out.

Ho: survivorship time distributions by history of incarceration, adjusting for clinic membership, is the same. 
Ha: survivorship time distributions are not equal.

Based on the p=0.04, we would reject the null hypothesis in lieu of the alternative.


```{r, results=TRUE}
survdiff (s.prison ~ prison + strata(clinic), data=addicts)

```

# Problem 2f

Sorry, ran out of time to try this by hand. 

At 4 months: 420 days (05% CI 376, 532)
At 8 months: 427 days (05% CI 323, 515)
At 12 months: 389 days (05% CI 301, 461)
```{r, results=TRUE}
s.addicts <- with(addicts, Surv(time, event))
getmedianres (s.addicts, times = 120, confint = TRUE)
getmedianres (s.addicts, times = 240, confint = TRUE)
getmedianres (s.addicts, times = 360, confint = TRUE)
```


## Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
